Stack Safety as a Security Property

### 2020-07-09 main.tex

\definition%{Stack Confidentiality}
%Let $\callmap$ be a call map and $\codemap$ a function map.
We say that a
system satisfies {\em stack confidentiality}
% with respect to $\callmap$ and $\codemap$
if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ 
in $\MPT$, the following holds. Let $\MPT_{\mathit{call}}$ be the prefix where
\(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} | \ret{\mach_c}\).
For each variant state \(\mach_e' \approx_{\mathit{Cof}(\mach_c,n)}
\mach_e\), let \(\machT\) be the similarly prefixed trace such that
\(\mach_e' \hookrightarrow \machT\). Then trace confidentiality holds on
\(\MPT_{\mathit{call}}\) and \(\machT\) with respect to \(\mathit{Cof}(\mach_c, n)\)
and \(R = \ret{\mach_c}\):

$$\forall \MPT_{\mathit{call}} ~ \machT. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machT ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, n) ~ (\ret{\mach_c}) ~ \MPT_{\mathit{call}} ~ \machT_{\mathit{call}}$$

\apt{oy. still needs work to make this intelligible}

@@

\definition%{Return Integrity}
A system enjoys {\em return integrity}
% with respect to a call map \(\callmap\) and return map \(\retmap\)
if, for any initial state pair 
$\mpstatename$ and any state pair \((\mach_c, \pol_c)\)
corresponding to a call in its induced trace, if
\(\mpstate{\mach_c}{\pol_c} \hookrightarrow \MPT\) and \(\mach_r\)
is the first unmatched return in $\MPT$, then $\mach_r$ corresponds
to a return state for $\mach_c$:

@@

      A system enjoys {\em observable stack integrity} with respect to
      \(\callmap\) and \(\codemap\) if for any initial state \(\mach_0\) and
      each transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\)
      and contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in \tainted,
      are not restored; every address that was varied and not changed in one
      of the executions is. So 108 contains 43 in the trace from \(\mach_r\),
      and after returning from {\tt g}, {\tt main} prints 85. But in the trace
      from \(\mach_r''\), 108 contains -4, and ultimately 38 is printed.
      So observable trace confidentiality does not hold. This example
      illustrates the weakness of observable confidentiality as a testing
      property; it takes until the very end of the program to determine whether
      a tainted value actually influences observable behavior.

>>>>

\definition%{Stack Confidentiality}
%Let $\callmap$ be a call map and $\codemap$ a function map.
We will say that a system satisfies {\em stack confidentiality} with respect to
\(\callmap\) in a similar way to stack integrity. For every initial state
\(\mach_0\), we take the induced trace \(\mpstate{\mach_0}{\pinit(\mach_0)}
\hookrightarrow \MPT\). Then for any \(n\)-transition
\(\mathit{Tr}_n ~ \MPT ~ \mpstate{\mach_c}{\pol_c} ~
\mpstate{\mach_e}{\pol_e}\), we take the prefix trace until return:
%
\[\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT_{call} | \ret{\mach_c}\]

We also take the corresponding trace from any variant \(\mach_e' 
\approx_{\mathit{Cof}(\mach_c,n)} \mach_e\):
%
\[\mach_e' \hookrightarrow \machT_{call} | \ret{\mach_c}\]

If, for all such pairs of traces, \(\propdef{TraceConfidentialiy} ~
\ret{\mach_c} ~ \MPT ~ \machT\), then the system as a whole enjoys
stack confidentiality with regard to \(\callmap\).

\apt{oy. still needs work to make this intelligible}
\sna{Attempted. There's a tension between introducing all the variables
     and keeping a good flow that I'm not sure I'm managing here though.}

@@

\definition%{Return Integrity}
A system enjoys {\em return integrity}
% with respect to a call map \(\callmap\) and return map \(\retmap\)
if, for any initial state pair 
$\mpstatename$ and any state pair \((\mach_c, \pol_c)\)
corresponding to a call in its induced trace, if
\(\mpstate{\mach_c}{\pol_c} \hookrightarrow \MPT\) and \(\mach_r\)
is the first unmatched return such that for some $\pol_r$
\[ \Unmatched ~ \MPT ~ (m_r,p_r)\MPT',\]
then $\mach_r$ corresponds to a return state for $\mach_c$:
\[\ret{\mach_c}\ \mach_r\]

@@

      A system enjoys {\em observable stack integrity} with respect to
      \(\callmap\) and \(\codemap\) if for any initial state \(\mach_0\) and
      each transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\)
      and contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109
      are not restored; every address that was varied and not changed in one
      of the executions is. So 108 contains 43 in the trace from \(\mach_r\),
      and after returning from {\tt g}, {\tt main} prints 85. But in the trace
      from \(\mach_r''\), 108 contains -4, and ultimately 38 is printed.
      So observable trace confidentiality does not hold. This example
      illustrates the weakness of observable confidentiality as a testing
      property; it takes until the very end of the program to determine whether
      a tainted value actually influences observable behavior.
